Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-06-20 paper.tex
Few corrections from Jean-Paul

\title{Locomotion and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach}

@@

This paper presents a general method for planning collision-free whole-body walking motions
for humanoid robots. First, we present a randomized algorithm for constrained motion
planning, that is used to generate collision-free statically stable paths solving
manipulation tasks. Then, we prove that these paths can always be approximated by collision-free
dynamically balanced trajectories. The proof is based on humanoid robot
\textit{small-space controllability} and leads to a sound algorithm presented
in the paper. We have  applied and evaluated our method
on several  problems where whole-body planning and  walk are needed,
and the results have been validated  on a real HRP-2 robot.

@@

\subsection{Walking Robot Controllability}
\label{sec:humanoid-ssc}

>>>>

\title{Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach}

@@

This paper presents a general method for planning collision-free whole-body walking motions
for humanoid robots. First, we present a randomized algorithm for constrained motion
planning, that is used to generate collision-free statically stable paths solving
manipulation tasks. Then, we show that dynamic walking makes humanoid robots 
small-space controllable. Such a property allows to easily transform 
collision-free statically stable paths into 
collision-free dynamically balanced trajectories. It leads to a sound 
algorithm which has been applied and evaluated on several
problems where whole-body planning and  walk are needed,
and the results have been validated  on a real HRP-2 robot.

@@

\subsection{Dynamic Walking Makes Humanoid Robots Small-Space Controllable}
\label{sec:humanoid-ssc}
